Haul-out behavior and aerial survey detectability of seals in the Bering and Chukchi seas

### 2022-01-13 analysis/paper/London_HauloutBeahvior.Rmd
COLOR PALETTE CHANGES
more use of metbrewer colorblind palettes and changes to better indicate overall reduced haul-out prob of bearded seals while still showing pattern

```{r setup, include = FALSE}
library(targets)
library(conflicted)
library(tidyverse)
conflict_prefer("filter", "dplyr")
conflict_prefer("select", "dplyr")
library(lubridate)
conflict_prefer("month","lubridate")
library(glue)
library(scales)
library(DBI)
library(dbplyr)
library(RPostgres)
library(pingr)
library(sf)
library(flextable)
library(patchwork)
library(rnaturalearth)
library(rnaturalearthdata)
library(ggspatial)
library(ggsci)
library(ggrepel)
library(gghighlight)
library(ggtext)
library(glmmLDTS)
library(mgcv)
library(ragg)
library(stickylabeller)

@@

ggplot(data = seal_hours_tbl, aes(x = yday, y = 1, fill = n))+
        geom_tile()+
        scale_fill_viridis_c(option="mako") +
        scale_x_continuous(breaks = c(60, 91, 121, 152, 182),
                           labels = c("01 March", "01 April", "01 May", "01 June", "01 July"),
                           expand = expansion(mult = c(0, 0))) +
        scale_y_continuous(expand = expansion(mult = c(0, 0))) +
  guides(fill = guide_colorbar(title.position = "bottom", 
                               title.hjust = 0.5, barwidth = 15,
                               barheight = 0.5)) +
  facet_grid(species ~ .) + 
  theme(axis.text.x = element_text(hjust = 0),
        axis.text.y = element_blank(),
        axis.title = element_blank(),
        panel.grid = element_blank(),
        legend.position = "bottom") +
  labs(fill = "seal-hours of bio-logger data") +
  ggtitle("Density of haul-out behavior observations varies from March through July",
          subtitle = "data are grouped by day-of-year and presented in seal-hours collated across years (2005-2020)")

@@

ggplot() +
  annotation_spatial(world, 
                     size = 0, 
                     fill = "grey70") +
  layer_spatial(
    data = locs_count, size = 0.125,
    aes(fill = ct)
  ) +
  scale_fill_distiller(type = "seq", palette = "YlOrRd", direction = 1,
                    trans = "log10", aesthetics = "fill",
    name = "number of locations",
    guide = guide_colorbar(title.position = "bottom", barwidth = 15, 
                           barheight = 0.5, title.hjust = 0.5)) + 
  facet_grid(~ species) +
  theme(legend.position = "bottom") +
  ggtitle("Spatial distribution of haul-out behavior data")
```

@@

```{r beardedHOCal, fig.height = 3.5, include=TRUE, fig.id = "beardedHOCal", fig.cap="Predicted haul-out probability of bearded seals (all ages and sex classes) from 1 March to 15 July for all and sex classes."}

@@

p <- ggplot(plot_df,aes(day,solar_hour,fill = ho_prob))+
  geom_tile(color= "white",size = 0) +
  scale_fill_viridis_c(name = "haul-out probability", aesthetics = "fill",
                       guide = guide_colorbar(title.position = "bottom", barwidth = 15,
                                              barheight = 0.5, title.hjust = 0.5)
  )
p <- p + facet_grid(age_sex~month)
p <- p + scale_x_continuous(breaks = c(1,10,20,30)) +
  scale_y_continuous(breaks = c(4,12,20))
p <- p + theme(legend.position = "bottom") +
  theme(strip.background = element_rect(colour="white")) +
  theme(axis.ticks=element_blank()) +
  xlab("day of month") + ylab("local solar hour") +
  ggtitle("Bearded seals rest on sea ice around solar noon and solar midnight")
p
```

@@

plot_df <- bearded_newdata %>%
  mutate(date = lubridate::as_date(yday, origin = "2015-01-01"),
         month = lubridate::month(date,label = TRUE),
         day = lubridate::day(date)) %>% 
  filter(age_sex != "YOUNG OF YEAR",
         between(solar_hour, 8,16)) %>% 
  group_by(age_sex)

plot_df_early <- plot_df %>% tidyr::nest() %>% 
  rowwise() %>% 
  mutate(peak_idx = which.max(data$ho_prob),
         peak_day = data$yday[peak_idx]) %>% ungroup() %>% 
  mutate(peak_avg = as.integer(mean(peak_day))) %>% 
  rowwise() %>% 
  mutate(data = list(data %>% filter(between(yday,(peak_avg-25)-3, (peak_avg-25)+3))),
         season = "early") %>% 
  unnest(cols = c(data))

plot_df_peak <- plot_df %>% tidyr::nest() %>% 
  rowwise() %>% 
  mutate(peak_idx = which.max(data$ho_prob),
         peak_day = data$yday[peak_idx]) %>% ungroup() %>% 
  mutate(peak_avg = as.integer(mean(peak_day))) %>% 
  rowwise() %>% 
  mutate(data = list(data %>% filter(between(yday,(peak_avg)-3, (peak_avg)+3))),
         season = "peak") %>% 
  unnest(cols = c(data))

plot_df_late <- plot_df %>% tidyr::nest() %>% 
  rowwise() %>% 
  mutate(peak_idx = which.max(data$ho_prob),
         peak_day = data$yday[peak_idx]) %>% ungroup() %>% 
  mutate(peak_avg = as.integer(mean(peak_day))) %>% 
  rowwise() %>% 
  mutate(data = list(data %>% filter(between(yday,(peak_avg+25)-3, (peak_avg+25)+3))),
         season = "late") %>% 
  unnest(cols = c(data))

plot_df <- bind_rows(list(plot_df_early, plot_df_peak, plot_df_late)) %>% 
  mutate(date_start = case_when(
    season == "peak" ~ format(lubridate::as_date(peak_avg, origin = "2015-01-01") - 3, "%d %b"),
    season == "early" ~ format(lubridate::as_date(peak_avg, origin = "2015-01-01") - 28, "%d %b"),
    season == "late" ~ format(lubridate::as_date(peak_avg, origin = "2015-01-01") + 22, "%d %b")
  )) %>% 
  mutate(date_end = case_when(
    season == "peak" ~ format(lubridate::as_date(peak_avg, origin = "2015-01-01") + 3, "%d %b"),
    season == "early" ~ format(lubridate::as_date(peak_avg, origin = "2015-01-01") - 22, "%d %b"),
    season == "late" ~ format(lubridate::as_date(peak_avg, origin = "2015-01-01") + 28, "%d %b")
  )) %>% 
  mutate(season = forcats::fct_relevel(season, "early", "peak", "late"),
         season = forcats::fct_recode(season, "peak haul out - 25 days" = "early",
                             "peak haul out" = "peak",
                             "peak haul out + 25 days" = "late"))

p_temp <- ggplot(plot_df, 
                 aes(temp2*27, ho_prob, color = age_sex, fill = age_sex)) +
  geom_pointrange(aes(ymin = lower95, ymax = upper95), alpha = 0.1, stroke = 0) +
  geom_smooth(method = "lm", formula = y ~ x, size = 0.3, alpha = 0.1,
              show.legend = FALSE) +
  scale_fill_d3() +
  scale_color_d3(guide = guide_legend(override.aes = list(alpha = 1),
                                      direction = "horizontal")) +
  theme(legend.title = element_blank(),
        legend.position = "none") +
  facet_wrap(. ~ season + date_start + date_end, scales = "free_x",
             labeller = label_glue('{season}\n{date_start} - {date_end}')) +
  xlab("temperature (C)") + ylab("haul-out probability")

p_wind <- ggplot(plot_df, aes(wind*10, ho_prob, color = age_sex, fill = age_sex)) +
  geom_pointrange(aes(ymin = lower95, ymax = upper95), alpha = 0.1, stroke = 0) +
  geom_smooth(method = "lm", formula = y ~ x, size = 0.3, alpha = 0.1,
              show.legend = FALSE) +
  scale_fill_d3() +
  scale_color_d3(guide = guide_legend(override.aes = list(alpha = 0.75),
                                      direction = "horizontal")) +
  facet_wrap(. ~ season + date_start + date_end, scales = "free_x",
             labeller = label_glue('{season}\n{date_start} - {date_end}')) +
  theme(legend.title = element_blank(),
        legend.position = "none") +
  xlab("total wind (m/s)") + ylab("haul-out probability")

library(patchwork)

p_temp / p_wind +
  plot_annotation(
    title = 'The influence of temperature and wind on predicted bearded seal \nhaul-out behavior varies within season',
    subtitle = 'data are subset to only include local solar hours between 0800 and 1600',
    caption = 'Solid lines represent linear fits to the predicted values and are \nprovided to better indicate underlying trends.')
```

@@

p <- ggplot(plot_df, aes(day,solar_hour,fill = ho_prob)) +
  geom_tile(color = "white",size = 0) +
  scale_fill_viridis_c(name = "haul-out probability", aesthetics = "fill",
                       guide = guide_colorbar(title.position = "bottom", barwidth = 15,
                                              barheight = 0.5, title.hjust = 0.5)
  )
p <- p + facet_grid(age_sex~month)
p <- p + scale_x_continuous(breaks = c(1,10,20,30)) +
  scale_y_continuous(breaks = c(4,12,20))
p <- p + theme(legend.position = "bottom") +
  theme(strip.background = element_rect(colour = "white")) +
  theme(axis.ticks = element_blank()) +
  xlab("day of month") + ylab("local solar hour") +
  ggtitle("Ribbon seals rest on sea ice in late spring and around solar noon.")
p
```

@@

plot_df <- ribbon_newdata %>%
  mutate(date = lubridate::as_date(yday, origin = "2015-01-01"),
         month = lubridate::month(date,label = TRUE),
         day = lubridate::day(date)) %>% 
  filter(age_sex != "YOUNG OF YEAR",
         between(solar_hour, 8,16)) %>% 
  group_by(age_sex)

plot_df_early <- plot_df %>% tidyr::nest() %>% 
  rowwise() %>% 
  mutate(peak_idx = which.max(data$ho_prob),
         peak_day = data$yday[peak_idx]) %>% ungroup() %>% 
  mutate(peak_avg = as.integer(mean(peak_day))) %>% 
  rowwise() %>% 
  mutate(data = list(data %>% filter(between(yday,(peak_avg-25)-3, (peak_avg-25)+3))),
         season = "early") %>% 
  unnest(cols = c(data))

plot_df_peak <- plot_df %>% tidyr::nest() %>% 
  rowwise() %>% 
  mutate(peak_idx = which.max(data$ho_prob),
         peak_day = data$yday[peak_idx]) %>% ungroup() %>% 
  mutate(peak_avg = as.integer(mean(peak_day))) %>% 
  rowwise() %>% 
  mutate(data = list(data %>% filter(between(yday,(peak_avg)-3, (peak_avg)+3))),
         season = "peak") %>% 
  unnest(cols = c(data))

plot_df_late <- plot_df %>% tidyr::nest() %>% 
  rowwise() %>% 
  mutate(peak_idx = which.max(data$ho_prob),
         peak_day = data$yday[peak_idx]) %>% ungroup() %>% 
  mutate(peak_avg = as.integer(mean(peak_day))) %>% 
  rowwise() %>% 
  mutate(data = list(data %>% filter(between(yday,(peak_avg+25)-3, (peak_avg+25)+3))),
         season = "late") %>% 
  unnest(cols = c(data))

plot_df <- bind_rows(list(plot_df_early, plot_df_peak, plot_df_late)) %>% 
  mutate(date_start = case_when(
    season == "peak" ~ format(lubridate::as_date(peak_avg, origin = "2015-01-01") - 3, "%d %b"),
    season == "early" ~ format(lubridate::as_date(peak_avg, origin = "2015-01-01") - 28, "%d %b"),
    season == "late" ~ format(lubridate::as_date(peak_avg, origin = "2015-01-01") + 22, "%d %b")
  )) %>% 
  mutate(date_end = case_when(
    season == "peak" ~ format(lubridate::as_date(peak_avg, origin = "2015-01-01") + 3, "%d %b"),
    season == "early" ~ format(lubridate::as_date(peak_avg, origin = "2015-01-01") - 22, "%d %b"),
    season == "late" ~ format(lubridate::as_date(peak_avg, origin = "2015-01-01") + 28, "%d %b")
  )) %>% 
  mutate(season = forcats::fct_relevel(season, "early", "peak", "late"),
         season = forcats::fct_recode(season, "peak haul out - 25 days" = "early",
                             "peak haul out" = "peak",
                             "peak haul out + 25 days" = "late"))

p_temp <- ggplot(plot_df, 
                 aes(temp2*27, ho_prob, color = age_sex, fill = age_sex)) +
  geom_pointrange(aes(ymin = lower95, ymax = upper95), alpha = 0.1, stroke = 0) +
  geom_smooth(method = "lm", formula = y ~ x, size = 0.3, alpha = 0.1,
              show.legend = FALSE) +
  scale_fill_d3() +
  scale_color_d3(guide = guide_legend(override.aes = list(alpha = 1),
                                      direction = "horizontal")) +
  theme(legend.title = element_blank(),
        legend.position = "none") +
  facet_wrap(. ~ season + date_start + date_end, scales = "free_x",
             labeller = label_glue('{season}\n{date_start} - {date_end}')) +
  xlab("temperature (C)") + ylab("haul-out probability")

p_wind <- ggplot(plot_df, aes(wind*10, ho_prob, color = age_sex, fill = age_sex)) +
  geom_pointrange(aes(ymin = lower95, ymax = upper95), alpha = 0.1, stroke = 0) +
  geom_smooth(method = "lm", formula = y ~ x, size = 0.3, alpha = 0.1,
              show.legend = FALSE) +
  scale_fill_d3() +
  scale_color_d3(guide = guide_legend(override.aes = list(alpha = 0.75),
                                      direction = "horizontal")) +
  facet_wrap(. ~ season + date_start + date_end, scales = "free_x",
             labeller = label_glue('{season}\n{date_start} - {date_end}')) +
  theme(legend.title = element_blank(),
        legend.position = "bottom") +
  xlab("total wind (m/s)") + ylab("haul-out probability")

library(patchwork)

p_temp / p_wind +
  plot_annotation(
    title = 'The influence of temperature and wind on predicted ribbon seal \nhaul-out behavior varies within season',
    subtitle = 'data are subset to only include local solar hours between 0800 and 1600',
    caption = 'Solid lines represent linear fits to the predicted values and are \nprovided to better indicate underlying trends.')
```

@@

p <- ggplot(plot_df,aes(day,solar_hour,fill=ho_prob))+
  geom_tile(color= "white",size = 0) +
  scale_fill_viridis_c(name = "haul-out probability", aesthetics = "fill",
                       guide = guide_colorbar(title.position = "bottom", barwidth = 15,
                                              barheight = 0.5, title.hjust = 0.5)
  )
p <- p + facet_grid(age_sex~month)
p <- p + scale_x_continuous(breaks = c(1,10,20,30)) +
  scale_y_continuous(breaks = c(4,12,20))
p <- p + theme(legend.position = "bottom") +
  theme(strip.background = element_rect(colour="white")) +
  theme(axis.ticks=element_blank()) +
  xlab("day of month") + ylab("local solar hour") +
  ggtitle("Spotted seals rest on sea ice in late spring and around solar noon.")
p
```

@@

plot_df <- spotted_newdata %>%
  mutate(date = lubridate::as_date(yday, origin = "2015-01-01"),
         month = lubridate::month(date,label = TRUE),
         day = lubridate::day(date)) %>% 
  filter(age_sex != "YOUNG OF YEAR",
         between(solar_hour, 8,16)) %>% 
  group_by(age_sex)

plot_df_early <- plot_df %>% tidyr::nest() %>% 
  rowwise() %>% 
  mutate(peak_idx = which.max(data$ho_prob),
         peak_day = data$yday[peak_idx]) %>% ungroup() %>% 
  mutate(peak_avg = as.integer(mean(peak_day))) %>% 
  rowwise() %>% 
  mutate(data = list(data %>% filter(between(yday,(peak_avg-25)-3, (peak_avg-25)+3))),
         season = "early") %>% 
  unnest(cols = c(data))

plot_df_peak <- plot_df %>% tidyr::nest() %>% 
  rowwise() %>% 
  mutate(peak_idx = which.max(data$ho_prob),
         peak_day = data$yday[peak_idx]) %>% ungroup() %>% 
  mutate(peak_avg = as.integer(mean(peak_day))) %>% 
  rowwise() %>% 
  mutate(data = list(data %>% filter(between(yday,(peak_avg)-3, (peak_avg)+3))),
         season = "peak") %>% 
  unnest(cols = c(data))

plot_df_late <- plot_df %>% tidyr::nest() %>% 
  rowwise() %>% 
  mutate(peak_idx = which.max(data$ho_prob),
         peak_day = data$yday[peak_idx]) %>% ungroup() %>% 
  mutate(peak_avg = as.integer(mean(peak_day))) %>% 
  rowwise() %>% 
  mutate(data = list(data %>% filter(between(yday,(peak_avg+25)-3, (peak_avg+25)+3))),
         season = "late") %>% 
  unnest(cols = c(data))

plot_df <- bind_rows(list(plot_df_early, plot_df_peak, plot_df_late)) %>% 
  mutate(date_start = case_when(
    season == "peak" ~ format(lubridate::as_date(peak_avg, origin = "2015-01-01") - 3, "%d %b"),
    season == "early" ~ format(lubridate::as_date(peak_avg, origin = "2015-01-01") - 28, "%d %b"),
    season == "late" ~ format(lubridate::as_date(peak_avg, origin = "2015-01-01") + 22, "%d %b")
  )) %>% 
  mutate(date_end = case_when(
    season == "peak" ~ format(lubridate::as_date(peak_avg, origin = "2015-01-01") + 3, "%d %b"),
    season == "early" ~ format(lubridate::as_date(peak_avg, origin = "2015-01-01") - 22, "%d %b"),
    season == "late" ~ format(lubridate::as_date(peak_avg, origin = "2015-01-01") + 28, "%d %b")
  )) %>% 
  mutate(season = forcats::fct_relevel(season, "early", "peak", "late"),
         season = forcats::fct_recode(season, "peak haul out - 25 days" = "early",
                             "peak haul out" = "peak",
                             "peak haul out + 25 days" = "late"))

p_temp <- ggplot(plot_df, 
                 aes(temp2*27, ho_prob, color = age_sex, fill = age_sex)) +
  geom_pointrange(aes(ymin = lower95, ymax = upper95), alpha = 0.1, stroke = 0) +
  geom_smooth(method = "lm", formula = y ~ x, size = 0.3, alpha = 0.1,
              show.legend = FALSE) +
  scale_fill_d3() +
  scale_color_d3(guide = guide_legend(override.aes = list(alpha = 1),
                                      direction = "horizontal")) +
  theme(legend.title = element_blank(),
        legend.position = "none") +
  facet_wrap(. ~ season + date_start + date_end, scales = "free_x",
             labeller = label_glue('{season}\n{date_start} - {date_end}')) +
  xlab("temperature (C)") + ylab("haul-out probability")

p_wind <- ggplot(plot_df, aes(wind*10, ho_prob, color = age_sex, fill = age_sex)) +
  geom_pointrange(aes(ymin = lower95, ymax = upper95), alpha = 0.1, stroke = 0) +
  geom_smooth(method = "lm", formula = y ~ x, size = 0.3, alpha = 0.1,
              show.legend = FALSE) +
  scale_fill_d3() +
  scale_color_d3(guide = guide_legend(override.aes = list(alpha = 0.75),
                                      direction = "horizontal")) +
  facet_wrap(. ~ season + date_start + date_end, scales = "free_x",
             labeller = label_glue('{season}\n{date_start} - {date_end}')) +
  theme(legend.title = element_blank(),
        legend.position = "bottom") +
  xlab("total wind (m/s)") + ylab("haul-out probability")

library(patchwork)

p_temp / p_wind +
  plot_annotation(
    title = 'The influence of temperature and wind on predicted spotted seal \nhaul-out behavior varies within season',
    subtitle = 'data are subset to only include local solar hours between 0800 and 1600',
    caption = 'Solid lines represent linear fits to the predicted values and are \nprovided to better indicate underlying trends.')
```

>>>>

```{r setup, include = FALSE}
library(targets)
library(conflicted)
library(tidyverse)
conflict_prefer("filter", "dplyr")
conflict_prefer("select", "dplyr")
library(lubridate)
conflict_prefer("month","lubridate")
library(glue)
library(scales)
library(DBI)
library(dbplyr)
library(RPostgres)
library(pingr)
library(sf)
library(flextable)
library(patchwork)
library(rnaturalearth)
library(rnaturalearthdata)
library(ggspatial)
library(ggsci)
library(ggrepel)
library(gghighlight)
library(ggtext)
library(glmmLDTS)
library(mgcv)
library(ragg)
library(stickylabeller)
library(MetBrewer)

@@

ggplot(data = seal_hours_tbl, aes(x = yday, y = 1, fill = n))+
        geom_tile()+
        scale_fill_gradientn(colors = rev(met.brewer("Hokusai2"))) +
        # scale_fill_viridis_c(option="mako") +
        scale_x_continuous(breaks = c(60, 91, 121, 152, 182),
                           labels = c("01 March", "01 April", "01 May", "01 June", "01 July"),
                           expand = expansion(mult = c(0, 0))) +
        scale_y_continuous(expand = expansion(mult = c(0, 0))) +
  guides(fill = guide_colorbar(title.position = "bottom", 
                               title.hjust = 0.5, barwidth = 15,
                               barheight = 0.5)) +
  facet_grid(species ~ .) + 
  theme(axis.text.x = element_text(hjust = 0),
        axis.text.y = element_blank(),
        axis.title = element_blank(),
        panel.grid = element_blank(),
        legend.position = "bottom") +
  labs(fill = "seal-hours of bio-logger data") +
  ggtitle("Density of haul-out behavior observations varies from March through July",
          subtitle = "data are grouped by day-of-year and presented in seal-hours collated across years (2005-2020)")

@@

ggplot() +
  annotation_spatial(world, 
                     size = 0, 
                     fill = "grey70") +
  layer_spatial(
    data = locs_count, size = 0.125,
    aes(fill = ct)
  ) +
  scale_fill_gradientn(colors = rev(met.brewer("Greek")),
                    trans = "log10", aesthetics = "fill",
    name = "number of locations",
    guide = guide_colorbar(title.position = "bottom", barwidth = 15, 
                           barheight = 0.5, title.hjust = 0.5)) + 
  facet_grid(~ species) +
  theme(legend.position = "bottom") +
  ggtitle("Spatial distribution of haul-out behavior data")
```

@@

```{r beardedHOCal, fig.height = 4.5, include=TRUE, fig.id = "beardedHOCal", fig.cap="Predicted haul-out probability of bearded seals (all ages and sex classes) from 1 March to 15 July for all and sex classes."}

@@

p <- ggplot(plot_df,aes(day,solar_hour,fill = ho_prob))+
  geom_tile(color= "white",size = 0) +
  scale_fill_gradientn(colors = rev(met.brewer("Hiroshige")),
                       name = "haul-out probability", aesthetics = "fill",
                       limits = c(0,1), breaks = c(0.25, 0.50, 0.75),
                       guide = guide_colorbar(title.position = "bottom", barwidth = 15,
                                              barheight = 0.5, title.hjust = 0.5)
  # scale_fill_viridis_c(name = "haul-out probability", aesthetics = "fill",
  #                      guide = guide_colorbar(title.position = "bottom", barwidth = 15,
  #                                             barheight = 0.5, title.hjust = 0.5)
  )
p <- p + facet_grid(age_sex~month)
p <- p + scale_x_continuous(breaks = c(1,10,20,30)) +
  scale_y_continuous(breaks = c(4,12,20))
p <- p + theme(legend.position = "bottom") +
  theme(strip.background = element_rect(colour="white")) +
  theme(axis.ticks=element_blank()) +
  xlab("day of month") + ylab("local solar hour") +
  ggtitle("Bearded seals rest on sea ice around solar noon and solar midnight")
p
```

@@

targets::tar_load(bearded_wx_plot, store = here::here("_targets"))

bearded_wx_plot
```

@@

p <- ggplot(plot_df, aes(day,solar_hour,fill = ho_prob)) +
  geom_tile(color = "white",size = 0) +
  scale_fill_gradientn(colors = rev(met.brewer("Hiroshige")),
                       name = "haul-out probability", aesthetics = "fill",
                       limits = c(0,1), breaks = c(0.25, 0.50, 0.75),
                       guide = guide_colorbar(title.position = "bottom", barwidth = 15,
                                              barheight = 0.5, title.hjust = 0.5)
  # scale_fill_viridis_c(name = "haul-out probability", aesthetics = "fill",
  #                      guide = guide_colorbar(title.position = "bottom", barwidth = 15,
  #                                             barheight = 0.5, title.hjust = 0.5)
  )
p <- p + facet_grid(age_sex~month)
p <- p + scale_x_continuous(breaks = c(1,10,20,30)) +
  scale_y_continuous(breaks = c(4,12,20))
p <- p + theme(legend.position = "bottom") +
  theme(strip.background = element_rect(colour = "white")) +
  theme(axis.ticks = element_blank()) +
  xlab("day of month") + ylab("local solar hour") +
  ggtitle("Ribbon seals rest on sea ice in late spring and around solar noon.")
p
```

@@

targets::tar_load(ribbon_wx_plot, store = here::here("_targets"))

ribbon_wx_plot
```

@@

p <- ggplot(plot_df,aes(day,solar_hour,fill=ho_prob))+
  geom_tile(color= "white",size = 0) +
  scale_fill_gradientn(colors = rev(met.brewer("Hiroshige")),
                       name = "haul-out probability", aesthetics = "fill",
                       limits = c(0,1), breaks = c(0.25, 0.50, 0.75),
                       guide = guide_colorbar(title.position = "bottom", barwidth = 15,
                                              barheight = 0.5, title.hjust = 0.5)
  # scale_fill_viridis_c(name = "haul-out probability", aesthetics = "fill",
  #                      guide = guide_colorbar(title.position = "bottom", barwidth = 15,
  #                                             barheight = 0.5, title.hjust = 0.5)
  )
p <- p + facet_grid(age_sex~month)
p <- p + scale_x_continuous(breaks = c(1,10,20,30)) +
  scale_y_continuous(breaks = c(4,12,20))
p <- p + theme(legend.position = "bottom") +
  theme(strip.background = element_rect(colour="white")) +
  theme(axis.ticks=element_blank()) +
  xlab("day of month") + ylab("local solar hour") +
  ggtitle("Spotted seals rest on sea ice in late spring and around solar noon.")
p
```

@@

targets::tar_load(spotted_wx_plot, store = here::here("_targets"))

spotted_wx_plot
```
